Supermartingales and Termination Analysis of Statistical PCF

### 2021-01-03 LICS21/confluent.tex
lead -> led; Ex. VI.2: minor

\changed[lo]{We are thus lead to consider the reduction relation on skeletons (and positions in a skeleton), which can be extended from the definitions on terms in the obvious way,} 
%The positions in a skeleton and the reduction relation on skeletons can be extended from the definitions on terms in the obvious way, 
with $\tif{\skeletonPlaceholder < 0}{A}{B}$ reducing nondeterministically to both $A$ and $B$, and $\tsample$ reducing to $\skeletonPlaceholder$.
For example, we have 
\(
(\lambda x . \tif{x < 0}{x}{\skeletonPlaceholder}) \, \tsample
\to
(\lambda x . \tif{x < 0}{x}{\skeletonPlaceholder}) \, \skeletonPlaceholder
\to
\tif{\skeletonPlaceholder < 0}{\skeletonPlaceholder}{\skeletonPlaceholder}
\to
\skeletonPlaceholder
\).

@@

\begin{example}[Labelling samples by terms]
Consider the terms
\begin{align*}
A[x] &= \tif{\tif{x>0}{I}{I} \, \tsample - 0.5 > 0}{0}{\Omega}\\
B &= \tif{\tsample - 0.5 > 0}{0}{\Omega}
\end{align*}
If terms rather than skeletons were used to label samples, the set of traces where $A[\tsample]$ terminates would be
\[\begin{array}{l}
\bigcup_{r \in [0,1]} \{s \in I^{L_s(A[\tsample])} \mid \\
\qquad\qquad\qquad\quad s([A[\tsample]], \mathsf{if}_1;\underline{-}_1;@_1;\mathsf{if}_1) = r, \\
\qquad\qquad\qquad\quad s([A[\tsample], A[\underline r], \ldots, B, \mathsf{if}_1) > 0.5 \}.
\end{array}\] 
\lo{We have just defined $L_0(M)$, but what is $L_s(\cdot)$ (subscript $s$)? I assume it is the version of $L_0(M)$ that labels samples by terms.}

>>>>

\changed[lo]{We are thus led to consider the reduction relation on skeletons (and positions in a skeleton), which can be extended from the definitions on terms in the obvious way,} 
%The positions in a skeleton and the reduction relation on skeletons can be extended from the definitions on terms in the obvious way, 
with $\tif{\skeletonPlaceholder < 0}{A}{B}$ reducing nondeterministically to both $A$ and $B$, and $\tsample$ reducing to $\skeletonPlaceholder$.
For example, we have 
\(
(\lambda x . \tif{x < 0}{x}{\skeletonPlaceholder}) \, \tsample
\to
(\lambda x . \tif{x < 0}{x}{\skeletonPlaceholder}) \, \skeletonPlaceholder
\to
\tif{\skeletonPlaceholder < 0}{\skeletonPlaceholder}{\skeletonPlaceholder}
\to
\skeletonPlaceholder
\).

@@

\begin{example}[Labelling samples by terms]
Consider the terms
\begin{align*}
A[x] &= \tif{\tif{x>0}{I}{I} \, \tsample - 0.5 > 0}{0}{\Omega}\\
B &= \tif{\tsample - 0.5 > 0}{0}{\Omega}
\end{align*}
If terms rather than skeletons were used to label samples, the set of traces where $A[\tsample]$ terminates would be
\[\begin{array}{l}
\bigcup_{r \in [0,1]} \Big\{s \in I^{L_s(A[\tsample])} \mid \\
\qquad\qquad\qquad\quad s([A[\tsample]], \mathsf{if}_1;\underline{-}_1;@_1;\mathsf{if}_1) = r, \\
\qquad\qquad\qquad\quad s([A[\tsample], A[\underline r], \ldots, B, \mathsf{if}_1) > 0.5 \Big\}.
\end{array}\] 
\lo{There are a number of spurious square bracket in the predicate of the set comprehension above.}

\lo{We have just defined $L_0(M)$, but what is $L_s(\cdot)$ (subscript $s$)? I assume it is the version of $L_0(M)$ that labels samples by terms.}
